Optimal (Multiway) Spatial Joins

### 2024-05-27 msj.tex
yufei

\extraspacing {\bf Set $\bm{H'}$.} Take any horizontal segment $h = [x_1, x_2] \times y \in H$. Let $p$ be the rightmost point on $h$ satisfying the condition that at least one rectangle in $R_{k-2}$ covers $p$. This $p$ exists if and only if $h$ has at least one left-end covering rectangle in $R_{k-2}$. If $p$ exists and has coordinates $(x, y)$, we refer to the segment $h' = [x_1, x] \times y$ as the {\em trimmed segment} of $h$; conversely, we call $h$ the {\em full segment} of $h'$.

@@

As mentioned in Section~\ref{sec:intro:prev}, 2-SJ can be solved in $F_2(n, \out) = O(n \log n + \out)$ time using a comparison-based algorithm. By Theorem~\ref{thm:main-recur}, in general, a comparison-based $(k-1)$-SJ algorithm with runtime $F_{k-1}(n, \out)$ spawns a comparison-based $k$-SJ algorithm whose running time $F_k(n, \out)$ obeys \eqref{eqn:main:reccurrence}. Specifically, for $k \ge 3$, there is a constant $c > 1$ such that
\myeqn{
    && F_{k}(n, \out) \nn \\
    &\le& c \cdot k^3 \cdot \big( F_{k-1}(n, \out) + n \log n + k \cdot \out \big) \nn \\
    &=& c^2 \cdot k^3(k-1)^3 \cdot (F_{k-2}(n,\out) + n\log n + k\cdot \out) + \nn \\
    && c \cdot k^3 \cdot (n\log n + k\cdot \out ) \nn\\
    &<& c^2 \cdot k^3(k-1)^3 \cdot F_{k-2}(n,\out) +  \nn\\
    && (c+c^2)\cdot k^3(k-1)^3 \cdot (n\log n + k \cdot\out) \nn \\
    &\leq& c^3 \cdot k^3(k-1)^3(k-2)^3 \cdot F_{k-3}(n,\out) + \nn\\
    && (c+c^2+c^3)\cdot k^3(k-1)^3(k-2)^3 \cdot (n\log n + k \cdot\out) \nn\\
    &\leq& ... \nn \\
    &\leq& c^{k-2} \cdot (k!)^3 \cdot F_{2}(n,\out) + \nn \\
    && \Big(\sum_{i =1}^{k-2}c^i \Big)\cdot (k!)^3 \cdot (n\log n + k \cdot\out) \nn \\
    &\leq & 2c^{k-1} \cdot (k!)^3 \cdot O(n\log n + k \cdot\out) \nn
}
which completes the proof of Theorem~\ref{thm:main-alg}.

>>>>

\extraspacing {\bf Set $\bm{H'}$.} Take any horizontal segment $h = [x_1, x_2] \times y \in H$. Let $p$ be the rightmost point on $h$ satisfying the condition that at least one left-end covering rectangle of $h$ in $R_{k-2}$ covers $p$. This $p$ exists if and only if $h$ has at least one left-end covering rectangle in $R_{k-2}$. If $p$ exists and has coordinates $(x, y)$, we refer to the segment $h' = [x_1, x] \times y$ as the {\em trimmed segment} of $h$; conversely, we call $h$ the {\em full segment} of $h'$.

@@

As mentioned in Section~\ref{sec:intro:prev}, 2-SJ can be solved in $F_2(n, \out) = O(n \log n + \out)$ time using a comparison-based algorithm. By Theorem~\ref{thm:main-recur}, in general, a comparison-based $(k-1)$-SJ algorithm with runtime $F_{k-1}(n, \out)$ spawns a comparison-based $k$-SJ algorithm whose running time $F_k(n, \out)$ obeys \eqref{eqn:main:reccurrence}. Specifically, for $k \ge 3$, there is a constant $c \ge 2$ such that
\myeqn{
    && F_{k}(n, \out) \nn \\
    &\le& c \cdot k^3 \cdot \big( F_{k-1}(n, \out) + n \log n + k \cdot \out \big) \nn \\
    &=& c^2 \cdot k^3(k-1)^3 \cdot (F_{k-2}(n,\out) + n\log n + k\cdot \out) + \nn \\
    && c \cdot k^3 \cdot (n\log n + k\cdot \out ) \nn\\
    &<& c^2 \cdot k^3(k-1)^3 \cdot F_{k-2}(n,\out) +  \nn\\
    && (c+c^2)\cdot k^3(k-1)^3 \cdot (n\log n + k \cdot\out) \nn \\
    &\leq& c^3 \cdot k^3(k-1)^3(k-2)^3 \cdot F_{k-3}(n,\out) + \nn\\
    && (c+c^2+c^3)\cdot k^3(k-1)^3(k-2)^3 \cdot (n\log n + k \cdot\out) \nn\\
    &\leq& ... \nn \\
    &\leq& c^{k-2} \cdot (k!)^3 \cdot F_{2}(n,\out) + \nn \\
    && \Big(\sum_{i =1}^{k-2}c^i \Big)\cdot (k!)^3 \cdot (n\log n + k \cdot\out) \nn \\
    &\leq & 2c^{k-1} \cdot (k!)^3 \cdot O(n\log n + k \cdot\out) \nn
}
which completes the proof of Theorem~\ref{thm:main-alg}.
